---
title: "Plot Generation"
author: "Kevin Robb"
date: "12/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Disclaimer

This file is for making plots to demonstrate points I make in talks and the design proposal about lag errors and overfitting. This data is not real and is being generated; I am NOT using it to proclaim fraudulent results or anything unethical. Ok now that that's out of the way, let's make some plots.

# Make noise

```{r}
size = 40
noise = runif(size, min=-8, max=8)
x = c(1:size)
plot(x,noise)
```


# Make data

```{r}
x = c(1:size)
y_true = x
y_meas = y_true + noise

# Make State for high Q (overfitting)
# follow the measurements
y_state_highQ = y_true + 0.75 * noise

# Make State for appropriate Q
# decrease reliance on measurements over time (converge to truth)
confidence = c(1:size)
y_state_goodQ = y_true + (size - confidence) / size * noise

# Make State for low Q (lag error)
# fall behind measurements
y_state_lowQ = 0.6 * y_true + 0.1 * noise
```


# Make the plots

```{r}
library(reshape2)
library(ggplot2)
library(grid)
library(gridExtra)
library(cowplot)

# use the data from above to make a dataframe
df <- data.frame(x,y_true,y_meas,y_state_highQ,y_state_goodQ,y_state_lowQ)
names(df) <- c("Time","Truth","Measurement","State_high","State","State_low")

# subset each variable
df_high = melt(df[,c(1,2,3,4)], id=c("Time"))
df_good = melt(df[,c(1,2,3,5)], id=c("Time"))
df_low = melt(df[,c(1,2,3,6)], id=c("Time"))

# make a plot just to get the legend
p_leg <- ggplot(df_good) + geom_line(aes(x=Time,y=value,colour=variable)) +
  scale_colour_manual(values=c("grey43","red","limegreen")) +
  ggtitle("Appropriate Q") + 
  cowplot::theme_minimal_grid(12)
legend <- cowplot::get_legend(p_leg)

# plot the three different states
p_high <- ggplot(df) + geom_line(aes(x=Time,y=Truth),col="grey43") +
  geom_point(aes(x=Time,y=Measurement),size=1,col="red") +
  geom_line(aes(x=Time,y=State_high),col="limegreen") +
  ggtitle("High Q (Overfitting)") + 
  cowplot::theme_minimal_grid(12) +
  theme(legend.position="none") + ylab("State Variable") + xlab("Time") +
  theme(axis.text.x=element_blank(),axis.text.y=element_blank(),axis.ticks=element_blank())

p_good <- ggplot(df) + geom_line(aes(x=Time,y=Truth),col="grey43") +
  geom_point(aes(x=Time,y=Measurement),size=1,col="red") +
  geom_line(aes(x=Time,y=State),col="limegreen") +
  ggtitle("Appropriate Q (Converges on Truth)") + 
  cowplot::theme_minimal_grid(12) +
  theme(legend.position="none") + ylab("State Variable") + xlab("Time") +
  theme(axis.text.x=element_blank(),axis.text.y=element_blank(),axis.ticks=element_blank())

p_low <- ggplot(df) + geom_line(aes(x=Time,y=Truth),col="grey43") +
  geom_point(aes(x=Time,y=Measurement),size=1,col="red") +
  geom_line(aes(x=Time,y=State_low),col="limegreen") +
  ggtitle("Low Q (Lag Error)") + 
  cowplot::theme_minimal_grid(12) +
  theme(legend.position="none") + ylab("State Variable") + xlab("Time") +
  theme(axis.text.x=element_blank(),axis.text.y=element_blank(),axis.ticks=element_blank())
```

# Combine plots

Want a 2x2 grid with the three plots and the legend

```{r}
p <- cowplot::plot_grid(p_good,legend,p_high,p_low,ncol=2)
p
```

# Save plot to file

```{r}
plot_path = "q_demo.png"
save_plot(plot_path,p)
```







